---
title: "Coding in R {intro}"
description: |
  An introduction to developing in R
author:
  - name: Zac Garland
date: 2021-10-23
preview: preview.png
output:
  distill::distill_article:
    self_contained: false
    theme: theme.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r,include=FALSE}
include_link <- function(href,alt = "link"){
  shiny::HTML(glue::glue("<a href=\"{href}\" target=\"_blank\">{alt}</a>"))
  
}
```


# Getting Started

First things first, lets take care of a few housekeeping items (like getting you up and running). 

Recommended setup:

- <b>Install R, RStudio, Tidyverse:</b> `r include_link('https://r4ds.had.co.nz/introduction.html#prerequisites')`
- <b>Install Rtools (windows):</b> `r include_link('https://cran.r-project.org/bin/windows/Rtools/history.html')`
- <b>Install Devtools:</b> `r include_link('https://devtools.r-lib.org/')`

 



To check that your environment is properly setup, run: 

```{r}
devtools::has_devel()
#> Your system is ready to build packages!
```


# TODO: What is R?

> R is a language and environment for statistical computing and graphics.

[R Project](https://www.r-project.org/about.html)




# TODO: Pros & Cons

# TODO: Workflow (packages & scripts)
```{r}

# usethis
# gert
# devtools
# tidyverse

create_new_package <- function(package_name, ...) {
  r_proj_dir <- path.expand("~/r_projects")
  if (!dir.exists(r_proj_dir)) dir.create(r_proj_dir)

  package_name <- package_name %>% make.names()

  usethis::create_tidy_package(file.path(r_proj_dir, package_name), ...)
}








```



# TODO: Data Viz
```{r}
# ggplot2
# plotly
# highcharter
# r2d3
# others
```



# TODO: Tibbles (data frames)



# TODO: Tidy Data

```{r}

# tidyr
# dplyr
# lubridate
# 

```


# TODO: Programming (iteration, functional vs OOP)
```{r}
# purrr
# furrr

```


# TODO: Financial Data

```{r}
# tidyquant
# quantmod
# 
```



# TODO: Modeling 
```{r}
# tidymodels
# fable
# forecast
```



# TODO: Rmarkdown Driven Everything

```{r}
# rmarkdown
# flexdashboard
# distill
# blogdown
# pkgdown

```


# TODO: Shiny

```{r}
# shiny
# shinyWidgets
# bslib
```


# TODO: HTML, CSS, JS

```{r}
# htmltools
# shiny
```


# TODO: HTML Widgets
```{r}
# htmlwidgets
# 
```


# TODO: Data Tables
```{r}
# kableExtra
# reactable

```


# TODO: Geospatial

```{r}
# leaflet
# highcharts.Maps
# plotly
# 


```



# Resources

The bible: [R for Data Science](https://r4ds.had.co.nz/)



