---
title: "Coding in R {intro}"
description: |
  An introduction to developing in R
author:
  - name: Zac Garland
date: 2021-10-23
preview: preview.png
output:
  distill::distill_article:
    self_contained: false
    theme: theme.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r,include=FALSE}
include_link <- function(href,alt = "link"){
  shiny::HTML(glue::glue("<a href=\"{href}\" target=\"_blank\">{alt}</a>"))
  
}
```


# Getting Started

First things first, lets take care of a few housekeeping items (like getting you up and running). 

Recommended setup:

- <b>Install R, RStudio, Tidyverse:</b> `r include_link('https://r4ds.had.co.nz/introduction.html#prerequisites')`
- <b>Install Rtools (windows):</b> `r include_link('https://cran.r-project.org/bin/windows/Rtools/history.html')`
- <b>Install Devtools:</b> `r include_link('https://devtools.r-lib.org/')`

 



To check that your environment is properly setup, run: 

```{r}
devtools::has_devel()
#> Your system is ready to build packages!
```


# TODO: What is R?

# TODO: Pros & Cons

# TODO: Workflow (packages & scripts)

# TODO: Data Viz

# TODO: Tibbles (data frames)

# TODO: Tidy Data

# TODO: Programming (iteration, functional vs OOP)

# TODO: Modeling 

# TODO: Rmarkdown Driven Everything

# TODO: Shiny

# TODO: HTML, CSS, JS




# Resources

The bible: [R for Data Science](https://r4ds.had.co.nz/)



