---
title: "Coding in R {tidy-intro}"
description: |
  An introduction to developing in R
author:
  - name: Zac Garland
date: 2021-10-23
preview: preview.png
categories:
  - Open Learning
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false
    theme: theme.css
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r,include=FALSE}
include_link <- function(href,alt = "link"){
  shiny::HTML(glue::glue("<a href=\"{href}\" target=\"_blank\">{alt}</a>"))
  
}
```


```{r, include = FALSE}
library(tidyverse)
```



# What is R?


### The technical definition: 

From the [R Project](https://www.r-project.org/about.html)

> R is a language and environment for statistical computing and graphics.


### My definition:

> R is an end-to-end data science language - rooted in statistics, data visualizations, and open education.


# Why I Picked R

Shortly after graduating, I worked for a fin-tech firm called FactSet. If you're not familiar, think of a well designed bloomberg. (dont worry, I like bloomberg too) 

Shortly after our initial training, we had guest speakers who shared their stories & the vision for each business unit. After hearing from the quant group... I knew what I wanted to do; & I pursued it. 

When we were assigned accounts, I was 😀. My clients had similar interests.

> one day, I received a voicemail. "hi zac, I was wondering if you could help us analyze our portfolios cluster risk. give me a call back."

<div class="callout">I had no idea what the hell cluster risk was.</div> But I wanted to find out. 

# One google search

<b>Q:</b> what is cluster risk? 

<b>A:</b> ~something I could analyze in python or R. 


For the next 6 months, I wrote code from 7-midnight. Most of it was... terrible. But I was hooked & I loved it. Eventually, I decided it was something I wanted to do full time. 

I left San Francisco, moved to a mountain town of 500 (spending most* of my life savings), and wrote the <a href="https://zacgarland.com/equity-research/" target="_blank">capstone</a> I had been thinking about for a year. 



I took the view - either it turns into a business, or it's proof of learning. 

> either way, it was something I had to do. 


# a few years later

A few years later, I'd like to share some of the knowledge I've gained from both personal & professional experience. 

- First - with the R community <b>that_gave_me_everything # :)</b>
- Second - with my team at Mastercard <b>#eitools</b>

> In the grand scheme of things, <b>I know; I know nothing</b> - which is ironically, the best part. As I learn, I'll do my best to share. 

# BUT

The first book you should read, understand, and utilize is [R for Data Science](https://r4ds.had.co.nz/data-visualisation.html#data-visualisation)

Start with the [Pre-Requisites](https://r4ds.had.co.nz/introduction.html#prerequisites) 

Then read r4ds cover to cover. do all of the exercises.

# THEN

Then, check out my posts when you have time.

<hr>
<hr>

# Dev Check

To check that your environment is properly setup to read the rest of my blog posts, please run:


```{r}
devtools::has_devel()

#> Your system is ready to build packages!
```



# My Blog Post Plan:


`r glue::glue("Last updated on: {Sys.Date()}")`

```{r, code_folding}
zg_blog_pm <- readr::read_csv(here::here("data/blog_post_pm.csv")) %>% 
  as.data.frame()

collapsibleTree::collapsibleTreeSummary(
  zg_blog_pm,
  hierarchy = c("group", "package"),
  collapsed = FALSE,
  height = "1000px",
  zoom = FALSE,
  fontSize = 14
)


```

